Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-11 README.Rmd
updated code file names

- `data-preparation.R` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the paper
- `figure-compression.R` contains R code for compressing the static figure used in the paper
- `submission-steps.R` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.

>>>>

- `data-preparation.Rmd` contains R code for preparing the raw bullet data (bullet training data, bullet testing data, and example matching signatures) to be used in the paper
- `figure-compression.Rmd` contains R code for compressing the static figure used in the paper
- `submission-steps.Rmd` contains the to do list and R code for preparing the files for submission to the ASA Data Science Journal.
